Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method

### 2019-09-25 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We have reported a favorable assessment of our formal synthesis method to obtain the optimal size of the PV system. 
Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and 
constitute future work: ($1$) improvement of the power reliability 
analysis: to include loss of load probability or loss of power 
supply probability, which can make the analysis more \textcolor{red}{precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, 
based on historical data}; 
($2$) the cost analysis is well-tailored to the Amazon region of Brazil; 
however, a broad analysis from other isolated areas must be 
performed to make the optimization general in terms 
of applicability \textcolor{red}{in other isolated areas of the world, as India and China, for example}; ($3$) to deploy at the field some PV systems 
sized using our synthesized results to validate it\textcolor{red}{, because a comparative with a real system may be more reliable than comparing with a simulation tool}.

>>>>

We have reported a favorable assessment of our formal synthesis method to obtain the optimal size of the PV system. 
Nevertheless, we have also identified three main threats to the validity of our experimental results, which can be further assessed and 
constitute future work: ($1$) improvement of the power reliability 
analysis: to include loss of load probability or loss of power 
supply probability, which can make the analysis more precise by considering the dynamic of the weather characteristics over the year or by electric load changes over time, 
based on historical data; 
($2$) the cost analysis is well-tailored to the Amazon region of Brazil; 
however, a broad analysis from other isolated areas must be 
performed to make the optimization general in terms 
of applicability in other isolated areas of the world, such as India and China; ($3$) to deploy at the field some PV systems 
sized using our synthesized results to validate it since a comparative with a real system may be more reliable than comparing with a simulation tool.
